Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-07-26 emsoft-2019/camera_ready/Motiv.tex
class is updated into acmsmall

% !TEX root = main.tex
\begin{figure}[t]
\centering
	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
	\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
	\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
	\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	{

		%\begin{center}
		%\hspace*{\fill} 
		\begin{tikzpicture}[auto,node distance=1cm,>=latex']
		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
		\node [block1,below = 0.8cm of RMPC] (highprec) {\Mahmoud{High-precision controller (\autoref{eq:affine_map})}};
		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
		\node [block3,below=.8cm of highprec,
		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
		\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=1cm] (decide) {$e\leq  \Delta$};
		\node [block3, below=0.8cm of decide,node distance=1cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
		\node [block2, right=1.3cm of decide,
		node distance=1cm] (delta) {$\Delta=e+\varepsilon_{SAFE}$};
		\node [block1,below = 0.8cm of done] (output) {Low-precision controller \Mahmoud{(\autoref{eq:affine_map})}};
		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
		\node at (9,-.25) {$e$};

@@

%
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller
with 14 regions, shown in~\autoref{fig:inverted_pendulum}(b).
A sample region with the corresponding affine map is shown below:
\begin{equation*}
\resizebox{.9\hsize}{!}{$
\begin{bmatrix}
-0.005  &0.999\\
-0.998  &-0.049\\
0.005  &-0.999\\
0.998   &0.049
\end{bmatrix}x_k\leq 
\begin{bmatrix}
0.416\\
3.157\\
0.617\\
-0.0124
\end{bmatrix}
\Rightarrow
u(x_k)=\begin{bmatrix}
0.05&-9.67
\end{bmatrix}x_k+4.02$}
\end{equation*}
where the output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. 
The remaining mappings have a similar structure.
For this new controller, the incorrect region selection error is 
approximately $e = 0.019$, which is now below the disturbance bound $\Delta_1$,
so that we can continue with the precision assignment.

>>>>

% !TEX root = main.tex
\begin{figure}[t]
%\centering
	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
	\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
	\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
	\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	%\begin{center}
	{

		%\centering
		%\hspace*{\fill} 
		\begin{tikzpicture}[auto,node distance=1cm,>=latex']
		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
		\node [block1,below = 0.8cm of RMPC] (highprec) {High-precision controller (\autoref{eq:affine_map})};
		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
		\node [block3,below=.8cm of highprec,
		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
		\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=1cm] (decide) {$e\leq  \Delta$};
		\node [block3, below=0.8cm of decide,node distance=1cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
		\node [block2, right=1.3cm of decide,
		node distance=1cm] (delta) {$\Delta=e+\varepsilon_{SAFE}$};
		\node [block1,below = 0.8cm of done] (output) {Low-precision controller (\autoref{eq:affine_map})};
		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
		%\node at (9,-.25) {$e$};

@@

%
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller
with 14 regions, shown in~\autoref{fig:inverted_pendulum}(b).
A sample region with the corresponding affine map is shown below:
\begin{equation*}
%\resizebox{.9\hsize}{!}{$
\begin{bmatrix}
-0.005  &0.999\\
-0.998  &-0.049\\
0.005  &-0.999\\
0.998   &0.049
\end{bmatrix}x_k\leq 
\begin{bmatrix}
0.416\\
3.157\\
0.617\\
-0.0124
\end{bmatrix}
\Rightarrow
u(x_k)=\begin{bmatrix}
0.05&-9.67
\end{bmatrix}x_k+4.02%$}
\end{equation*}
where the output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. 
The remaining mappings have a similar structure.
For this new controller, the incorrect region selection error is 
approximately $e = 0.019$, which is now below the disturbance bound $\Delta_1$,
so that we can continue with the precision assignment.

### 2019-07-26 emsoft-2019/camera_ready/RMPC_Daisy.tex
class is updated into acmsmall

\begin{figure}[t]
\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
...
elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
return $v_k$
\end{lstlisting}
\caption{Structure of an explicit MPC controller}
\label{lst:caseof}
\end{figure}
%Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.

>>>>

\begin{figure}[t]
%\begin{center}
%\begin{tabular}{c}
\begin{lstlisting}[mathescape=true,frame=lines,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
...
elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
return $v_k$
\end{lstlisting}
%\end{tabular}
%\end{center}
\caption{Structure of an explicit MPC controller}
\label{lst:caseof}
\end{figure}
%Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
